How residence time constrains diversity

### 2015-06-20 paper/Manuscript.Rmd
finishing up Results -KL

*Autocorrelated residence times and right-skewed residence time distributions—*The probabilistic and complex modeling approach produced all primary expected results, signifying that predictions of otherwise simplistic and idealized chemostat theory could arise in a complex system. Residence times of individuals, resource particles, inert tracers, and most any non-permanent component of the system were highly correlated (Fig 1). Likewise, residence time distributions were right-skewed and well approximated by lognormal and power-law models (e.g. Pareto, Zipf, Zipf-Mandelbrot) (Fig 2). We also observed the expected  hump-shaped relationship of *N* to residence time, revealing that residence time could be low enough to exclude reproduction and high enough to result in a rate of resource supply that could not support optimal growth.

@@

*Total abundance (N)*—

>>>>

**Simplistic theory supported in complex systems**
The probabilistic and complex modeling approach produced all primary expected results, signifying that predictions of otherwise simplistic and idealized chemostat theory could arise in a complex system.

*Autocorrelated residence times—*Residence times of individuals, resource particles, inert tracers, and most any non-permanent component of the system were highly correlated (Fig 1).

*Autocorrelated residence times and right-skewed residence time distributions—*Likewise, residence time distributions were right-skewed and well approximated by lognormal and power-law models (e.g. Pareto, Zipf, Zipf-Mandelbrot) (Fig 2).

*Abundance-residence time relationship—*We also observed the expected hump-shaped relationship of *N* to residence time, revealing that residence time could be low enough to exclude reproduction and high enough to result in a rate of resource supply that could not support optimal growth.

@@
